\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=3cm]{geometry}
\usepackage{url}
\usepackage{dirtree}
\usepackage{xcolor}


\begin{document}


\newcommand{\ttilde}[0]{\raisebox{0.5ex}{\texttildelow}}

\begin{center}
 \huge{\textbf{Turing Award recipients}}\\[.5em]
 \Large{Project 2 Overview}
\end{center}
\vspace{3em}
\tableofcontents

\newpage
\section{Introduction}
This document will provide some information about our project (`Turing Award Recipients`). It also contains our CSS template and the website main features.
The address of the GIT repository is: \url{@atelier.inf.usi.ch:/home/lambrr/project_sa1.git}

\vspace{2em}

\section{Roles}
\begin{tabular}{p{.275\linewidth} p{.65\linewidth}}
\textbf{Team leaders:} & Michele Dalle Rive, Sofia d'Atri\\[.3em]
                        &\textbf{Duties:} Coordinate the team and check for the quality of everyone's work.\\[.5em]
\textbf{CSS leaders:} & Alessandro Zanzi, George Batyrev\\[.3em]
                        &\textbf{Duties:} Choose the color pallette and create consistent, organized and commented CSS code.\\[.5em]
\textbf{Topic leaders:} & Michele Smaldone, Filippo Piloni,\newline Giorgio Bonetto, Federico Bonezzi\\[.3em]
                        &\textbf{Duties:} Choose relevant content for the website and assign a subtopic to each team member.\\[.5em]
\textbf{Git leader:} & Riccardo Lambrugo\\[.3em]
                        &\textbf{Duties:} Organize correctly the GIT remote repository, keeping track of the commits and handling any problems.\\[.5em]
\textbf{Bonus teams:} & To be defined\\[.3em]
\textbf{Inactive members:} & Buonaventura, Gur, Liang, Liu, Singh
\end{tabular}

\vspace{2em}
\section{Communication channels}
WhatsApp groups:
\begin{itemize}
 \item \textbf{Group 2 SA:} Chat group with all team members
 \item \textbf{Group 2 Leaders:} Chat group with Team, CSS, Topic and GIT Leaders
 \item \textbf{Topic Leaders:} Chat group for the Topic Leaders
\end{itemize}
Discord server with different text and voice channel for CSS discussion, GIT discussion, Topic discussion, HTML discussion and general discussion.


\newpage

\section{Website organization}

The 55 years of Turing Award are divided among the topic leaders:
\begin{itemize}
 \item \textbf{Topic leader 1:} 1966\ -\ 1979
 \item \textbf{Topic leader 2:} 1980\ -\ 1992
 \item \textbf{Topic leader 3:} 1993\ -\ 2006
 \item \textbf{Topic leader 4:} 2007\ -\ 2020
\end{itemize}
Each topic leader will assign one or many years to each team member.
\\[1em]
The website will contain the following pages:
\begin{itemize}
 \item \texttt{/index.html}: Homepage of the website containing a timeline.
 \item \texttt{/html/about.html}: Page containing general information about the Award.
 \item Decade pages: 7 pages containing the winners for each decade (1960s - 2020s).
 \item Winner pages: 55 pages (1 per year) containing the reason for that year award.
 \item Biography pages: 27-55 pages (1 per year) containing a concise biography about that year's winners
\end{itemize}
Each Turing Award year has 2 HTML pages (Reason for the win and biography of the winners), so each team member will be assigned roughly to 2 Turing Award years.\\
The total amount of pages will be \ttilde93-120 pages.





\newpage

\section{Repository organization}
\dirtree{%
.1 ./src/.
.2 index.html.
.2 css.
.3 index.css.
.3 colors.css.
.3 biography.css.
.3 core.css.
.3 decade.css.
.3 ....
.2 html.
.3 decade.html (template).
.3 decades.
.4 1980.
.5 1980s.html (decade page).
.5 1981.html.
.5 1982.html.
.5 ....
.4 ....
.3 about.html.
.3 ....
.2 documentation.
.3 inception.
.4 inception.tex.
.4 inception.pdf.
.3 ....
.2 js.
.3 ....
.2 images.
.3 logo.png.
.3 decades.
.4 1960.
.4 1970.
.5 1970.png.
.5 1971.png.
.5 ....
.4 1980.
.4 ....
.3 ....
}

\newpage
\section{CSS Layout}
The files contained in the \texttt{/src/css/} folder are the stylesheets for the different pages:
\begin{itemize}
 \item \texttt{core.css}: Contains shared styles in the whole website
 \item \texttt{colors.css}: Contains the color palette definition in order to be changed easily
 \item \texttt{index.css}: Contains the style for the homepage.
 \item \texttt{biography.css}: Contains the style for the biography of the winners
 \item \texttt{decade.css}: Contains the style for the pages about each decade.
\end{itemize}
\vspace{.5em}
The current color palette is:\\[.4em]
\fcolorbox[HTML]{000000}{293241}{\rule{0pt}{6pt}\rule{6pt}{0pt}}\quad Primary \& Background color.\\[.69em]
\fcolorbox[HTML]{000000}{98c1d9}{\rule{0pt}{6pt}\rule{6pt}{0pt}}\quad Secondary color.\\[.69em]
\fcolorbox[HTML]{000000}{e0fbfc}{\rule{0pt}{6pt}\rule{6pt}{0pt}}\quad Text color.\\[.69em]
\fcolorbox[HTML]{000000}{ee6c4d}{\rule{0pt}{6pt}\rule{6pt}{0pt}}\quad Accent color.\\
\end{document}
